Twists of supersymmetric gauge theories

### 2020-01-07 paper.tex

\begin{definition}
A \defterm{free BV theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
Q_{BV} \colon \cE \to \cE [1] 
\]
such that $(1)$: $Q_{BV}^2 = 0$ and $(2)$: the pair $(\cE , Q_{BV})$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to \Dens_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{BV} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{BV} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{definition}

@@

The BV bracket enjoys the graded skew symmetry property
\[
\{F, G\} = (-1)^{|F| |G|} \{G, F\}
\]
as well as the graded Jacobi identity.
This bracket together wtih $Q_{BV}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
Since the space of local functionals is not an algebra, the bracket does not satisfy any type of Leibniz rule.

\begin{definition}
A \defterm{classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
\[I \in \oloc^+(\cE)\]
of cohomological degree zero satisfying the Maurer-Cartan equation
\[Q_{BV} I + \frac{1}{2} \{I,I\} = 0 .\]
\end{definition}

Given a classical field theory $(E, Q_{BV}, \omega, I)$ we denote by
\[S = \frac{1}{2} \int_M \omega(e, Q_{BV} e) + I\in \oloc(E)\]
the BV action of the theory.

\begin{remark}
The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\] 
In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely $Q, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ satisfying the classical master equation.
The operator $Q_{BV}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
Because of this, we will sometimes refer to $(E, S, \omega)$ as the data of a classical field theory.
\end{remark}

\begin{remark}
We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q$ is simply an odd operator.
\end{remark}

@@

\begin{definition}
A \defterm{morphism} $F\colon (E, Q_{BV}, \omega, I) \rightsquigarrow (E', Q_{BV}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e. a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{BV}, Q_{BV}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{BV})\rightarrow (\cE', Q_{BV}')$ is a quasi-isomorphism. A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
\end{definition}

@@

\pavel{Chris, I think your diagrams of BV complexes would fit well here, can you insert them?}

@@

In this section we define what it means for a (super) Lie algebra to act on a classical field theory. Let $(E, Q_{BV},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra. Consider the graded vector space
\[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
\brian{not crazy about the notation $C^\bu(\fg, \oloc(\cE))$ for just the graded vector space before knowing that $\oloc$ is a module.}
parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
where $x_j \in \fg$. 
We follow the sign conventions of \cite{SafronovCoisoInt}, so the Chevalley--Eilenberg differential on $C^\bullet(\fg, \oloc(\cE))$ is given by the formula
\[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n)\]
and the degree $+1$ BV bracket by the formula
\[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
where $S_{k, l}$ is the set of $(k, l)$-shuffles, $\epsilon$ is the usual Koszul sign and
\[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
The operator $Q_{BV}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
\[
(Q_{BV} f)(x_1,\ldots, x_n) = Q_{BV} f(x_1,\ldots, x_n) 
\]
where $f : \fg^{\otimes n} \to \oloc(\cE)$. 
The differentials $\d_{CE}$ and $Q_{BV}$ are compatible in the sense that $(\d_{CE} + Q_{BV})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{BV}$. 
Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.

\begin{definition}
\label{infinitesimal_action_def}
Let $(E, Q_{BV},\omega, I)$ be a classical field theory. 
\begin{itemize}
\item[(1)]
An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{BV}, \omega, I)$ is an element of cohomological degree zero 
\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \in C^\bullet(\fg, \oloc(\cE)),\]
where $I_\fg^{(k)} : \fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
\begin{itemize}
\item[(a)] $I_\fg^{(0)} = I$;
\item[(b)] for each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields;
\item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
\[(\d_{CE} + Q_{BV}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
\end{itemize}
\item[(2)]
For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
An action $I_\fg$ is \defterm{elliptic} if the induced linear differential operator
\[
Q_{BV} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
\]
is elliptic as a $C^\bu(\fg)$-linear differential operator.
\end{itemize}
\end{definition}

@@

\begin{rmk}
We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $I_\fg$.
Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{BV} + \{I_\fg, -\}$ 
defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
By assumption that the Noether current is at least quadratic in the fields, we see that this differential defines a family of maps
\[
\fg^{\otimes k} \otimes \cE^{\otimes \ell} \to \cE
\]
combining to give $\cE$ the structure of an $L_\infty$-module for $\fg$.
\end{rmk}

@@

\begin{definition}
\label{group_action_def}
Let $(E, Q_{BV}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$. An \defterm{action} of $G$ on $(E, Q_{BV}, \omega, I)$ is given by the following data:
\begin{itemize}
\item An action of $G$ on $\cE$ compatible with the $G$-action on $M$.

@@

From a classical BRST theory $(\cF, S_{BRST})$, one can construct a classical BV theory as follows. Let $\{\ell_k\}_{k\geq 1}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.

First, we define the free BV theory. Split $S_{BRST} = S^{free}_{BRST} + I_{BRST}$, where $I_{BRST}\in\oloc^+(\cF)$ and $S^{free}_{BRST}$ is a quadratic local functional which we may view as defining a map
\[S^{free}_{BRST}\colon F\rightarrow F^!.\]
The underlying bundle of the BV theory is
\[
E = F \oplus F^! [-1].
\]
The differential of the free BV theory is
\[
Q_{BV} = \ell_1 + S^{free}_{BRST}.
\]
The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.

The interacting theory is constructed as follows. First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p\colon \cE\rightarrow \cF$. These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
\[
I_F (e) = \sum_{k \geq 2} \frac{1}{(k+1)!} \int_M \omega_F(e, (p^*\ell_k) (e, \ldots, e))
\] 
which is linear along $\cF^!$. Likewise, the BRST action $I_{BRST}$ pulls back to $\cE$, and we define the BV interaction as the sum
\[
I = I_{F} + p^* I_{BRST} \in \oloc^+(\cE) .
\]

\begin{lemma}
Suppose $(F, S_{BRST})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{BV}, \omega, I)$ is a classical BV theory.
\end{lemma}

We refer to the classical BV theory $(E, Q_{BV}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$. In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.

@@

\begin{definition} \label{def:twisting}
Suppose $(E, Q_{BV}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum. The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{BV} + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
\end{definition}

@@

\item (2 supercharges). This theory exists in dimensions 2 through 3 and it depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.

\item ($\cN_+$ supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$.

@@

Since we are working near the trivial connection, the topological term $\int F\wedge F\wedge \omega^3$ is exact, so we will drop it. The BV action of the twisted theory $S_{BV}$ is then the sum of the following terms:
\begin{align*}
S_{BRST} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
S_{anti} &= \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
I^{(1)} &= \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^* + \frac{1}{2}\Lambda F_{1, 1} \chi^* \\
I^{(2)} &= -\frac{1}{4}\int \frac{\chi^*}{\omega^5/5!} \chi^*.
\end{align*}

\begin{thm}
The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills is perturbatively equivalent to the holomorphic Chern--Simons theory on $\CC^5$ equipped with a Calabi--Yau structure $\Omega$ with the space of fields $\map(\CC^5, B\gg)$.
\label{thm:10dholomorphictwist}
\end{thm}
\begin{proof}
First, we may integrate out $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}. So, the above theory is perturbatively equivalent to the theory without $\chi$ and $\chi^*$ with the BV action
\begin{align*}
S_{\text{no }\chi} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
&+ \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
&+ \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^*
\end{align*}

@@

We decompose the fields with respect to $\U(5) \hookrightarrow \SO(6)$:
\begin{align*}
c & \mapsto A^0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
A & \mapsto A^{1,0} + A^{0,1} \in \Omega^{1,0}(\CC^3 ; \fg) \oplus \Omega^{0,1}(\CC^3) \\
\lambda & \mapsto \lambda^0_1 w_1 + \lambda_2^0 w_2 + A^{0,2} w_1 +  \Tilde{\lambda}^{0,2} w_2\in \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \\
\phi & \mapsto A 
\end{align*} 
where the $A^{\bu, \bu}, \lambda^{\bu,\bu}, \Tilde{\lambda}^{\bu,\bu}$ are all $\fg$-valued forms.

>>>>

\begin{definition}
A \defterm{free BV theory} on a manifold $M$ is the data:
\begin{itemize}
\item a finite rank $\ZZ\times\ZZ/2$-graded vector bundle $E \to M$ equipped with an even differential operator of cohomological degree $+1$
\[
Q_{\mr{BV}} \colon \cE \to \cE [1] 
\]
such that $(1)$: $Q_{\mr{BV}}^2 = 0$ and $(2)$: the pair $(\cE , Q_{\mr{BV}})$ is an elliptic complex;
\item a map of bundles
\[
\omega\colon E \otimes E \to \Dens_M [-1]
\]
that is
\begin{enumerate}
\item[$(1)$] fiberwise nondegenerate,
\item[$(2)$] graded skew symmetric, and
\item[$(3)$] satisfies $\int_M \omega(e_0, Q_{\mr{BV}} e_1) = (-1)^{|e_0|} \int_M \omega(Q_{\mr{BV}} e_0, e_1)$ where $e_i$ are compactly supported sections of $E$ .
\end{enumerate}
\end{itemize}
\end{definition}

@@

The BV bracket enjoys the graded skew symmetry property
\[
\{F, G\} = (-1)^{|F| |G|} \{G, F\}
\]
as well as the graded Jacobi identity.
This bracket together wtih $Q_{\mr{BV}}$ endows $\oloc(\cE)[-1]$ with the structure of a dg Lie algebra. 
Since the space of local functionals is not an algebra, the bracket does not satisfy any type of Leibniz rule.

\begin{definition}
A \defterm{classical BV field theory} (or simply, classical field theory) is a free BV theory $(E, Q, \omega)$ equipped with an even functional
\[I \in \oloc^+(\cE)\]
of cohomological degree zero satisfying the Maurer-Cartan equation
\[Q_{\mr{BV}} I + \frac{1}{2} \{I,I\} = 0 .\]
\end{definition}

Given a classical field theory $(E, Q_{\mr{BV}}, \omega, I)$ we denote by
\[S = \frac{1}{2} \int_M \omega(e, Q_{\mr{BV}} e) + I\in \oloc(E)\]
the BV action of the theory.

The local functional $S$ satisfies the {\em classical master equation} \[\{S, S\} = 0.\] 
In fact, given a degree $(-1)$ nondegenerate pairing $\omega$ on $E$, prescribing the data of a classical field theory (namely $Q, I$ satisfying the Maurer-Cartan equation) is equivalent to prescribing a local functional $S \in \oloc(\cE)$ satisfying the classical master equation.
The operator $Q_{\mr{BV}}$ is the BV bracket with the quadratic part of the BV action $S$, and the cubic and higher terms in $S$ coincide with $I$.
Because of this, we will sometimes refer to $(E, S, \omega)$ as the data of a classical field theory.

\begin{remark}
We will also consider \defterm{$\ZZ/2$-graded classical field theories} which are defined as before, but where $E$ has only a single $\ZZ/2$-grading and, correspondigly, $Q_{\mr{BV}}$ is simply an odd operator.
\end{remark}

@@

\begin{definition}
A \defterm{morphism} $F\colon (E, Q_{\mr{BV}}, \omega, I) \rightsquigarrow (E', Q_{\mr{BV}}', \omega', I')$ of classical field theories over the same manifold $M$ is a nonlinear map of vector bundles $E\rightsquigarrow E'$, i.e. a collection $F=\sum_{n\geq 1}^\infty F$ of poly-differential operators $F_n\colon \Sym^n(E)\rightarrow E'$, that intertwines the differentials $Q_{\mr{BV}}, Q_{\mr{BV}}'$, the pairings $\omega, \omega'$, and the interactions $I,I'$. A morphism is a \defterm{perturbative equivalence} if the map $F_1\colon (\cE, Q_{\mr{BV}})\rightarrow (\cE', Q_{\mr{BV}}')$ is a quasi-isomorphism. A classical field theory is \defterm{perturbatively trivial} if it is perturbatively equivalent to the zero theory ($E = 0$).
\end{definition}

@@

\pavel{Chris, I think your diagrams of BV complexes would fit well here, can you insert them?} \chris{I'm not sure exactly which diagrams you mean.  Can you clarify?}

@@

In this section we define what it means for a (super) Lie algebra to act on a classical field theory. Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory and $\fg$ a super Lie algebra. Consider the graded vector space
\[C^\bullet(\fg, \oloc(\cE)) = \bigoplus_n \hom(\wedge^n \fg, \oloc(\cE))[-n]\]
\brian{not crazy about the notation $C^\bu(\fg, \oloc(\cE))$ for just the graded vector space before knowing that $\oloc$ is a module.}
parametrizing multilinear maps $f\colon \fg^{\otimes n}\rightarrow \oloc(\cE)$ which satisfy the antisymmetry property
\[f(x_1, \dots, x_i, x_{i+1}, \dots, x_n) = -(-1)^{|x_1||x_2|} f(x_1, \dots, x_{i+1}, x_i, \dots, x_n)\]
where $x_j \in \fg$. 
We follow the sign conventions of \cite{SafronovCoisoInt}, so the Chevalley--Eilenberg differential on $C^\bullet(\fg, \oloc(\cE))$ is given by the formula
\[(\d_{CE} f)(x_1, \dots, x_n) = \sum_{i < j}(-1)^{|x_i| \sum_{p=1}^{i-1} |x_p| + |x_j| \sum_{p=1,p\neq i}^{j-1} |x_p| +i+j+|f|} f([x_i, x_j], x_1, \dots, \widehat{x}_i, \dots, \widehat{x}_j, \dots, x_n)\]
and the degree $+1$ BV bracket by the formula
\[\{f, g\}(x_1, \dots, x_{k+l}) = \sum_{\sigma\in S_{k, l}} \mathrm{sgn}(\sigma) (-1)^{\epsilon+\epsilon_1} \{f(x_{\sigma(1)}, \dots, x_{\sigma(k)}), g(x_{\sigma(k+1)}, \dots, x_{\sigma(k+l)})\},\]
where $S_{k, l}$ is the set of $(k, l)$-shuffles, $\epsilon$ is the usual Koszul sign and
\[\epsilon_1 = |g|k + \sum_{i=1}^k |x_{\sigma(i)}|(l+|g|).\]
The operator $Q_{\mr{BV}}$ on $\oloc(\cE)$ extends $C^\bu(\fg)$-linearly to an operator on $C^\bullet(\fg, \oloc(\cE))$ by the rule
\[
(Q_{\mr{BV}} f)(x_1,\ldots, x_n) = Q_{\mr{BV}} f(x_1,\ldots, x_n) 
\]
where $f : \fg^{\otimes n} \to \oloc(\cE)$. 
The differentials $\d_{CE}$ and $Q_{\mr{BV}}$ are compatible in the sense that $(\d_{CE} + Q_{\mr{BV}})^2 = 0$ making $C^\bu(\fg, \oloc(\cE))$ into a cochain complex with total differential $\d_{CE} + Q_{\mr{BV}}$. 
Via the BV bracket, the shift of this cochain complex $C^\bu(\fg, \oloc(\cE))[-1]$ is a dg Lie algebra.

\begin{definition}
\label{infinitesimal_action_def}
Let $(E, Q_{\mr{BV}},\omega, I)$ be a classical field theory. 
\begin{itemize}
\item[(1)]
An \defterm{action} of a super Lie algebra $\fg$ on $(E, Q_{\mr{BV}}, \omega, I)$ is an element of cohomological degree zero 
\[I_\fg = \sum_{k\geq 0} I_{\fg}^{(k)} \in C^\bullet(\fg, \oloc(\cE)),\]
where $I_\fg^{(k)} : \fg^{\otimes k} \to \oloc(\cE)$, that satisfies the following three conditions:
\begin{itemize}
\item[(a)] $I_\fg^{(0)} = I$;
\item[(b)] for each $k \geq 1$ and $x_1, \ldots, x_k \in \fg$ the local functional $I^{(k)}_\fg (x_1,\ldots, x_k)$ is at least quadratic in the fields;
\item[(c)] $I_\fg$ satisfies the Maurer--Cartan equation:
\[(\d_{CE} + Q_{\mr{BV}}) I_\fg + \frac{1}{2} \{I_\fg, I_\fg\} = 0.\]
\end{itemize}
\item[(2)]
For each $k \geq 1$ there is a decomposition $I_\fg^{(k)} = \sum_{\ell} I_\fg^{(k),\ell}$ where $ I_\fg^{(k),\ell}(x_1,\ldots,x_k) \in \oloc(\cE)$ is $\ell$-linear in the fields $\cE$ for all $x_1,\ldots,x_k \in \fg$.
An action $I_\fg$ is \defterm{elliptic} if the induced linear differential operator
\[
Q_{\mr{BV}} + \sum_{k \geq 1} \{I_\fg^{(k),2}, -\}
\]
is elliptic as a $C^\bu(\fg)$-linear differential operator.
\end{itemize}
\end{definition}

@@

\begin{rmk}
We have defined an action of a Lie algebra on a classical field theory in terms of a Noether current $I_\fg$.
Such data gives rise to an $L_\infty$ action of $\fg$ on the space of fields $\cE$ in the following way.
By the Maurer-Cartan equation, the operator $\d_{CE} + Q_{\mr{BV}} + \{I_\fg, -\}$ 
defines a differential on the graded vector space $\cO(\fg[1] \oplus \cE)$. 
By assumption that the Noether current is at least quadratic in the fields, we see that this differential defines a family of maps
\[
\fg^{\otimes k} \otimes \cE^{\otimes \ell} \to \cE
\]
combining to give $\cE$ the structure of an $L_\infty$-module for $\fg$.
\end{rmk}

@@

\begin{definition}
\label{group_action_def}
Let $(E, Q_{\mr{BV}}, \omega, I)$ be a classical field theory and $G$ is a supergroup acting on spacetime $M$. An \defterm{action} of $G$ on $(E, Q_{\mr{BV}}, \omega, I)$ is given by the following data:
\begin{itemize}
\item An action of $G$ on $\cE$ compatible with the $G$-action on $M$.

@@

From a classical BRST theory $(\cF, S_{\mr{BRST}})$, one can construct a classical BV theory as follows. Let $\{\ell_k\}_{k\geq 1}$ be the $L_\infty$ structure maps underlying the local Lie algebra $F[-1]$.

First, we define the free BV theory. Split $S_{\mr{BRST}} = S^{\mr{free}}_{\mr{BRST}} + I_{\mr{BRST}}$, where $I_{\mr{BRST}}\in\oloc^+(\cF)$ and $S^{\mr{free}}_{\mr{BRST}}$ is a quadratic local functional which we may view as defining a map
\[S^{\mr{free}}_{\mr{BRST}}\colon F\rightarrow F^!.\]
The underlying bundle of the BV theory is
\[
E = F \oplus F^! [-1].
\]
The differential of the free BV theory is
\[Q_{\mr{BV}} = \ell_1 + S^{free}_{BRST}.
\]
The BV pairing $\omega$ on $E$ is defined in terms of the natural pairing between $F$ and $F^!$.

The interacting theory is constructed as follows. First, note that for $k \geq 2$ the $L_\infty$ structure maps $\{\ell_k\}_{k \geq 2}$ on $\cF$ pull back to multilinear maps on $\cE$ via the obvious projection $p\colon \cE\rightarrow \cF$. These structure maps assemble into a local functional $I_F \in \oloc^+(\cE)$ defined by
\[
I_F (e) = \sum_{k \geq 2} \frac{1}{(k+1)!} \int_M \omega_F(e, (p^*\ell_k) (e, \ldots, e))
\] 
which is linear along $\cF^!$. Likewise, the BRST action $I_{\mr{BRST}}$ pulls back to $\cE$, and we define the BV interaction as the sum
\[
I_{\mr{BV}} = I_{F} + p^* I_{\mr{BRST}} \in \oloc^+(\cE) .
\]

\begin{lemma}
Suppose $(F, S_{\mr{BRST}})$ is a classical BRST theory such that $(\cE, Q)$ defined above is an elliptic complex. Then $(E, Q_{\mr{BV}}, \omega, I)$ is a classical BV theory.
\end{lemma}

We refer to the classical BV theory $(E, Q_{\mr{BV}}, \omega, I)$ from the above statement as the \defterm{$(-1)$-shifted cotangent bundle} of $\cF$ and by abuse of notation we often denote it simply by $\cE = T^*[-1] \cF$. In the case $S_{BRST} = 0$ we refer to the theory $T^*[-1] \cF$ as a theory of \defterm{cotangent type}.

@@

\begin{definition} \label{def:twisting}
Suppose $(E, Q_{\mr{BV}}, \omega, I)$ is a supersymmetric classical field theory and $(Q, \alpha)$ is a twisting datum. The \defterm{$Q$-twisted classical field theory} is the classical field theory $(E^Q, Q_{\mr{BV}} + \{\rho_2(Q), -\}, \omega, I + \rho_3(Q) + \dots)$, where
\[E^Q = \bigoplus_{n=-\infty}^\infty \Pi^n E(n)[-n]\]
for $E(n)$ the component of $E$ which has $\alpha$-weight $n$.
\end{definition}

@@

\item (2 supercharges). This theory exists in dimensions 2 through 3 and it depends on a Lie algebra $\fg$ together with an orthogonal $\fg$-representation $P$.
\end{itemize}

There are a few additional possibilities that occur in dimension 2.

\begin{itemize}
\item ($\cN_+$ supercharges, chiral supersymmetry). This theory exists in dimension 2 and depends on a Lie algebra $\fg$.

@@

Since we are working near the trivial connection, the topological term $\int F\wedge F\wedge \omega^3$ is exact, so we will drop it. The BV action of the twisted theory $S_{\mr{BV}}$ is then the sum of the following terms:
\begin{align*}
S_{\mr{BRST}} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2 + \chi \Lambda(\ol\dd_{A_{0, 1}}\psi) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [\chi, c]\chi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
I^{(1)} &= \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^* + \frac{1}{2}\Lambda F_{1, 1} \chi^* \\
I^{(2)} &= -\frac{1}{4}\int \frac{\chi^*}{\omega^5/5!} \chi^*.
\end{align*}

\begin{thm}
The holomorphic twist of 10d $\mc N=(1, 0)$ super Yang--Mills is perturbatively equivalent to the holomorphic Chern--Simons theory on $\CC^5$ equipped with a Calabi--Yau structure $\Omega$ with the space of fields $\map(\CC^5, B\gg)$.
\label{thm:10dholomorphictwist}
\end{thm}

\begin{proof}
First, we may integrate out $\chi$ and $\chi^*$ using Proposition \ref{prop:integrateoutfield}. So, the above theory is perturbatively equivalent to the theory without $\chi$ and $\chi^*$ with the BV action
\begin{align*}
S_{\text{no }\chi} &= \int \frac{\omega^5}{5!} \left(-(F_{2, 0}, F_{0, 2}) + (B, \dd_{A_{1, 0}} \psi)\right)  + \frac{1}{2}B\wedge \ol\dd_{A_{0, 1}} B\wedge\Omega \\
&+ \int \dd_{A_{1, 0}} c\wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [\psi, c]\wedge \psi^* + [B, c]\wedge B^* + \frac{1}{2}[c, c]c^* \\
&+ \int \psi\wedge A_{1, 0}^* + F_{0, 2}\wedge B^*
\end{align*}

@@

We decompose the fields with respect to $\mr U(5) \hookrightarrow \SO(6)$:
\begin{align*}
c & \mapsto A^0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
A & \mapsto A^{1,0} + A^{0,1} \in \Omega^{1,0}(\CC^3 ; \fg) \oplus \Omega^{0,1}(\CC^3) \\
\lambda & \mapsto \lambda^0_1 w_1 + \lambda_2^0 w_2 + A^{0,2} w_1 +  \Tilde{\lambda}^{0,2} w_2\in \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \\
\phi & \mapsto A 
\end{align*} 
where the $A^{\bu, \bu}, \lambda^{\bu,\bu}, \Tilde{\lambda}^{\bu,\bu}$ are all $\fg$-valued forms.
